---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# anthroplus

<!-- badges: start -->
[![R-CMD-check](https://github.com/WorldHealthOrganization/anthroplus/workflows/R-CMD-check/badge.svg)](https://github.com/WorldHealthOrganization/anthroplus/actions)
<!-- badges: end -->

The goal of `anthroplus` is to provide R functions for the application of
the WHO Reference 2007 for 5-19 years to monitor the growth of school-age
children and adolescents.

It is modeled after the [R Macros of the WHO Reference 2007](https://www.who.int/tools/growth-reference-data-for-5to19-years/application-tools).

## Installation

You can install the released version of anthroplus from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("anthroplus")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dirkschumacher/anthroplus")
```
## Example

### Z-scores

This function calculates z-scores for the three anthropometric indicators, 
weight-for-age, height-for-age and body mass index (BMI)-for-age.

```{r example}
library(anthroplus)
anthroplus_zscores(
  sex = c("1", "f"),
  age_in_months = c(100, 110),
  height_in_cm = c(100, 90),
  weight_in_kg = c(30, 40)
)
```

The returned value is a `data.frame` that can further be processed or
saved as a `.csv` file as in the original function.

You can also use the function with a given dataset with `with`

``` r
your_data_set <- read.csv("my_survey.csv")
with(
  your_data_set,
  anthroplus_zscores(
    sex = sex, age_in_months = age,
    weight_in_kg = weight, height_in_cm = height, 
    oedema = oedema
  )
)
```

### Prevalence estimates

The prevalence estimates are similar to `anthroplus_zscores`: again they
take vectors instead of a data frame and column names for the
aforementioned reasons.

```{r example2}
set.seed(1)
anthroplus_prevalence(
  sex = c(1, 2),
  age_in_months = rpois(100, 100),
  height_in_cm = rnorm(100, 100, 10),
  weight_in_kg = rnorm(100, 40, 10)
)[, c(1, 4, 5, 6)]
```
Using the function `with` it is easy to apply `anthroplus_prevalence` to a
full dataset.

To look at all parameters, type `?anthroplus_prevalence`.

### Contribution

Contributions in the form of issues are very welcome. In particular if you
find any bugs.

### Using the package in your own analyses

The package has been tested thoroughly, but we cannot guarantee that
there aren’t any bugs nor comes this with any warranty (as with all open
source software). If you find a bug or cannot reproduce results obtained
with other implementations, please post an issue.
