---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# anthroplus

<!-- badges: start -->
[![R-CMD-check](https://github.com/WorldHealthOrganization/anthroplus/workflows/R-CMD-check/badge.svg)](https://github.com/WorldHealthOrganization/anthroplus/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/anthroplus)](https://CRAN.R-project.org/package=anthroplus)
<!-- badges: end -->

The goal of `anthroplus` is to provide R functions for the application of
the WHO Reference 2007 for 5-19 years to monitor the growth of school-age
children and adolescents.

It is modeled after the [R Macros of the WHO Reference 2007](https://www.who.int/tools/growth-reference-data-for-5to19-years/application-tools).

## Installation

You can install the released version of anthroplus from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("anthroplus")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("worldhealthorganization/anthroplus")
```
## Example

### Z-scores

This function calculates z-scores for the three anthropometric indicators, 
weight-for-age, height-for-age and body mass index (BMI)-for-age.

```{r example}
library(anthroplus)
anthroplus_zscores(
  sex = c("1", "f"),
  age_in_months = c(100, 110),
  height_in_cm = c(100, 90),
  weight_in_kg = c(30, 40)
)
```

The functions support a `z_precision` parameter to control the number of
decimal places returned for z-scores. `z_precision` must be an integer
literal (for example `3L` or `4L`). By default z-scores are returned with
two decimal places; set `z_precision` to a higher integer literal when you
need more precision in the results.

```{r example-zprecision}
anthroplus_zscores(
  sex = c("1", "f"),
  age_in_months = c(100, 110),
  height_in_cm = c(100, 90),
  weight_in_kg = c(30, 40),
  z_precision = 4L
)
```

The returned value is a `data.frame` that can further be processed or
saved as a `.csv` file.

You can also use the function with a given dataset with `with`

``` r
your_data_set <- read.csv("my_survey.csv")
with(
  your_data_set,
  anthroplus_zscores(
    sex = sex_column, age_in_months = age_column,
    weight_in_kg = weight_column, height_in_cm = height_column,
    oedema = oedema_column
  )
)
```

### Prevalence estimates

The function to compute the prevalence estimates is similar 
to `anthroplus_zscores` in terms of the parameters.

```{r example2}
set.seed(1)
anthroplus_prevalence(
  sex = c(1, 2),
  age_in_months = rpois(100, 100),
  height_in_cm = rnorm(100, 100, 10),
  weight_in_kg = rnorm(100, 40, 10)
)[, c(1, 4, 5, 6)]
```

The `anthroplus_prevalence` function also accepts `z_precision` which will
control how z-scores displayed within prevalence tables are rounded. `z_precision`
must be an integer literal (for example `3L`). Use `z_precision` when you
need prevalence outputs that display z-scores with more than the default
two decimal places.

```{r example-prevalence-zprecision}
anthroplus_prevalence(
  sex = c(1, 2),
  age_in_months = rpois(100, 100),
  height_in_cm = rnorm(100, 100, 10),
  weight_in_kg = rnorm(100, 40, 10),
  z_precision = 3L
)[, c(1, 4, 5, 6)]
```

Using the function `with` it is easy to apply `anthroplus_prevalence` to a
full dataset.

To look at all parameters, type `?anthroplus_prevalence`.

### Contributions

Contributions in the form of issues are very welcome. In particular if you
find any bugs or cannot reproduce results obtained with other implementations.
